Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-08 paper.tex
edited intro

        \section{Open-science Platforms}\label{platforms}
            Efficient processing of workflows are only but a small portion of 
            the Big Data issue in neuroscience. % nice transition, this section gives more context for your study
            Sharing and storing of datasets
            and tools, secure access to and configuration of multiple computing 
            sites and provenance capture of all activities must be managed by 
            the researcher. This puts a heavy burden on researchers as they 
            require some knowledge of all these components in order to manage it
            correctly. These platforms also play a vital role in promoting 
            research through the sharing of knowledge. Users can choose to share
            their data and pipelines with others, reducing the need for others 
            to collect their own data or to develop their own workflows. It 
            also promotes robustness of results as the data and workflows will 
            be shared and tested by multiple users.

@@

            Examples of popular neuroinformatics open-science platforms include 
            CBRAIN\note{cite paper}, OpenNeuro \note{cite poster} and Neurodata
            \note{cite prepring}. OpenNeuro and NeuroData primarily focus on
            cloud deployement whereas CBRAIN is configured for the deployment
            of workflows on HPC resources. All three of these systems allow 
            users to configure, manage, share and execute their workflows with 
            the help of a web-based GUI. Integration with compute resources is
            entirely abstracted by the platforms. These platforms additionally
            provide tools to visualize their data.

@@

        \section{Infrastructure}\label{infrastructure}
            HPC infrastructure was designed during a time when compute resources
            were scarce. As a result, \tristan{I disagree with 'As a result' and I don't particularly agree with the previous sentence: even if
            resources aren't scarce, they are good reasons to optimize resource managers: energy consumption, application makespan, fairness, etc. Also,
            I'm not sure if resources are less scarce now than they used to be: with the rise of computational sciences, almost every researcher now
            needs a cluster, and Compute Canada (but also other infrastructures) has been very busy.}
            resource managers for these systems employ
            strategies to efficiently use the compute resources available for 
            processing. However, with the advent of big data, there has been a 
            shift from compute-intensive to data-intensive workloads. That is, 
            with the accumulation of large datasets, data transfers have begun 
            to monopolize processing time, and with it software has been 
            designed to minimize data transfers.

            We define HPC systems as those that employ shared parallel 
            filesystem such as Lustre \tristan{and data-unaware schedulers?}.
            \tristan{You should say that this definition is 'by contrast to big data platforms' to explain where it's coming from.}
            This shared filesystem is the slowest of
            all storage devices as it is shared amongst all users of the system.
            Compute nodes in an HPC system may or may not contain any local 
            storage and network interconnects between nodes are typically fast.
            Resources managers used in HPC infrastructures typically employ 
            batch scheduling and execute heterogenous workflows. 
            Examples of schedulers used in HPC clusters 
            include SLURM, PBS, SGE and HTCondor \note{cite here}.

            Commodity infrastructure \tristan{Call it 'Big Data infrastructure?'} differs from HPC infrastructures in that
            it uses less-costly hardware. It follows a shared-nothing paradigm
            where the storage is not shared between nodes. That is, all compute
            nodes are responsible for storing the data as well. File systems
            used in these clusters are distributed filesystems, such as the
            Hadoop Distributed File System (HDFS) and Alluxio \note{cite}.
            Fault-tolerance of the data is achieved through replication across
            nodes. As transferring data across the network is typically costly 
            in such infrastructures, frameworks designed to run on commodity 
            infrastructure attempt to limit the transfer of data across nodes. 
            Resource managers created specifically for these systems
            typically expect dedicated infrastructure, as is the case with 
            Yet Another Resource Negotiator (YARN), but can also execute 
            heterogeneous workflows, as can be seen with Mesos \note{cite}.

            Commodity clusters may also come in the form of cloud infrastructure.
            While the hardware employed is typically the same as other
            commodity clusters, the software used varies. Cloud infrastructures
            have the added benefit of virtualization, allowing users to 
            configure the infrastructure and software requirements to meet their
            needs. Cloud infrastructure also enables researchers to request
            dedicated resources without having to maintain these resources. One
            of the biggest limiting factors of cloud resources is the cost 
            associated with usage.

            Researchers typically have access to HPC infrastructure, but may
            also have access to commodity infrastructure in the format of a 
            local cluster or cloud. Although both neuroimaging frameworks and
            big data frameworks can be made to execute in either environments,
            the performance improvements that they bring are very much 
            dependent on infrastructure that they are executed on. For instance,
            neuroimaging workflows typically read and write to a shared file
            system at each workflow step. This is less of an issue in HPC 
            infrastructure as network bandwidth is typically better than on 
            commodity infrastructure. In contrasts, Big Data framework typically
            rely on there being some form of local storage. Employing a Big Data
            framework on HPC infrastructure may in turn result in less to no 
            data locality -- a strategy employed by Big Data frameworks to 
            minimize data movement across the network. Due to the variability in
            infrastructure available to researchers, a workflow framework good
            for neuroscience must be well adapted to handle these differences.

>>>>

        \section{Open-science Platforms}\label{platforms}
            Efficient processing of workflows is only but a small portion of 
            the Big Data issue in neuroscience. % nice transition, this section gives more context for your study
            Sharing and storing of datasets
            and tools, secure access to and configuration of multiple computing 
            sites and provenance capture of all activities must be managed by 
            the researcher. This puts a heavy burden on researchers as they 
            require some knowledge of all these components in order to manage it
            correctly. These platforms also play a vital role in promoting 
            research through the sharing of knowledge. Users can choose to share
            their data and pipelines with others, reducing the need for others 
            to collect their own data or to develop their own workflows. It 
            also promotes robustness of results as the data and workflows will 
            be shared and tested by multiple users.

@@

            Examples of popular neuroinformatics open-science platforms include 
            CBRAIN~\cite{10.3389/fninf.2014.00054}, 
            OpenNeuro~\cite{gorgolewski2017openneuro} and 
            Neurodata~\cite{burns2018community}. OpenNeuro and NeuroData primarily focus on
            cloud deployement whereas CBRAIN is configured for the deployment
            of workflows on HPC resources. All three of these systems allow 
            users to configure, manage, share and execute their workflows with 
            the help of a web-based GUI. Integration with compute resources is
            entirely abstracted by the platforms. These platforms additionally
            provide tools to visualize their data.

@@

        \section{Infrastructure}\label{infrastructure}
            HPC infrastructure was initially designed for the processing of 
            compute-intensive applications. As a result, \tristan{I disagree with 'As a result' and I don't particularly agree with the previous sentence: even if
            resources aren't scarce, they are good reasons to optimize resource managers: energy consumption, application makespan, fairness, etc. Also,
            I'm not sure if resources are less scarce now than they used to be: with the rise of computational sciences, almost every researcher now
            needs a cluster, and Compute Canada (but also other infrastructures) has been very busy.}
            resource managers for these systems employ
            strategies to efficiently use the compute resources available for 
            processing. However, with the advent of big data, data-intensive 
            workflows are now beginning to become more present on HPC systems.
            Since the schedulers and workflow engines made for HPC systems are 
            'data-unaware', they are not efficient with the processing of Big
            Data

            HPC and Big Data infrastructure differ in many ways. We define HPC 
            systems as those that employ a shared parallel 
            filesystem (distinct from any compute node), such as Lustre, and 
            data-unaware schedulers. \tristan{and data-unaware schedulers?}.
            \tristan{You should say that this definition is 'by contrast to big data platforms' to explain where it's coming from.}
            The shared parallel filesystem is the slowest of
            all storage devices found on HPC as it is shared amongst all users 
            of the system.
            Compute nodes in such infrastructure may not contain any local 
            storage. However, network interconnects between nodes are typically 
            fast.
            Resources managers used in HPC infrastructures typically employ 
            batch scheduling and execute heterogenous workflows. 
            Examples of schedulers used in HPC clusters 
            include SLURM~\cite{yoo2003slurm}, 
            PBS~\cite{10.1007/3-540-60153-8_34}, SGE~\cite{SGE} and 
            HTCondor~\cite{htcondor}.

            Big Data infrastructure \tristan{Call it 'Big Data infrastructure?'} differs from HPC infrastructures in that
            it uses less-costly hardware. It follows a shared-nothing paradigm
            where the storage is not shared between nodes. That is, all compute
            nodes are responsible for storing the data as well. File systems
            used within such infrastructure are distributed filesystems, such 
            as the
            Hadoop Distributed File System (HDFS)~\cite{5496972} and 
            Alluxio~\cite{Li:2014:TRM:2670979.2670985}.
            Fault-tolerance of the data is achieved through replication across
            nodes. As transferring data across the network is typically costly 
            in such infrastructures, frameworks designed to run on Big Data 
            infrastructure attempt to limit the transfer of data across nodes. 
            Resource managers created specifically for these systems
            typically expect dedicated infrastructure, as is the case with 
            Yet Another Resource Negotiator 
            (YARN)~\cite{Vavilapalli:2013:AHY:2523616.2523633}, but can also 
            execute heterogeneous workflows, as can be seen with 
            Mesos~\cite{hindman2011mesos}.

            Big Data infrastructure may also come in the form of cloud 
            infrastructure.
            While the hardware employed is typically the same as other
            Big Data clusters, the software used varies. Cloud infrastructures
            have the added benefit of virtualization, allowing users to 
            configure the infrastructure and software requirements to meet their
            needs. Cloud infrastructure also enables researchers to request
            dedicated resources without having to maintain these resources. One
            of the biggest limiting factors of cloud resources is the cost 
            associated with usage~\cite{10.3389/fninf.2017.00063}.

            Researchers typically have access to HPC infrastructure, but may
            also have access to Big Data infrastructure in the format of a 
            local cluster or cloud. Although both neuroimaging frameworks and
            Big Data frameworks can be configured to execute in either 
            environments,
            the performance enhancements that they bring are extremely
            dependent on infrastructure that they are executed on. For instance,
            neuroimaging workflows typically read and write to a shared file
            system at each workflow step. This is less of an issue in HPC 
            infrastructure as network bandwidth is typically better than on 
            commodity infrastructure. In contrasts, Big Data framework typically
            rely on there being some form of local storage. Employing a Big Data
            framework on HPC infrastructure may in turn result in less to no 
            data locality -- a strategy employed by Big Data frameworks to 
            minimize data movement across the network. Due to the variability in
            infrastructure available to researchers, a workflow framework good
            for neuroscience must be well adapted to handle these differences.
